---
title: "Alpha Diversity"
author: "'[Dominique G. Maucieri](https://dominiquemaucieri.com), [Samuel Starko](https://samstarko.wordpress.com/)"
  and [Julia K. Baum](https://www.juliakbaum.org/)'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
subtitle: 'Data and R code accompanying: Tipping points and interactive effects of
  human disturbance and heat stress on coral reef communities'
---


```{r Set up environment, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, tidy = TRUE, message=FALSE)

#Loading packages
library(here)
library(dplyr)
library(tidyr)
library(xlsx)
library(kableExtra)
library(iNEXT)
library(ggplot2)
library(cowplot)
library(glmmTMB)
library(strucchange)

#My ggplot theme
theme_DGM <- function () { 
  theme_classic(base_size=14) + 
    theme(panel.border = element_blank(), 
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          axis.line = element_line(colour = "black"), 
          axis.title=element_text(size=16, face="bold"), 
          axis.text = element_text(size=14, face="plain"), 
          legend.text=element_text(size=14, face="plain"), 
          legend.title = element_text(size=16, face="bold"))
}

load(file = here("data", "Alpha_Diversity.RData"))

before_years <- c("2013", "2014", "2015a", "2015b")
after_years <- c("2016b", "2017")

```

# Summary of the Data

```{r Summary of Data}

#Summary of the data
print("total # of years")
length(unique(Alpha_Diversity_df$Year))
print("total # of sites")
length(unique(Alpha_Diversity_df$Site))
print("total # of site - year combinations")
length(unique(Alpha_Diversity_df$SiteYear))
print("total # of quadrats")
length(unique(Alpha_Diversity_df$UniqueID))

```
## Table S1
```{r Sample sizes}

#Sample Sizes
Table_S1 <- Alpha_Diversity_df %>% dplyr::group_by(Year, Site) %>% dplyr::summarise(Sample_Size = length(Quadrat)) %>%
  mutate(Site = factor(Site, levels = c("VL2", "VL1", "VL5", "L5", "M10", "L1", "H2", "VH3", "VH1", "VH2",
                                        "L4", "M3", "M2", "M1", "M4", "M6", "VL3"))) %>% arrange(Site) %>%
  tidyr::spread(Year, Sample_Size)
Table_S1[is.na(Table_S1)] <- 0

Table_S1 %>%
  kbl() %>%
  kable_styling()

#Run to save Table S1 as an excel sheet
# write.xlsx(as.data.frame(Table_S1), here::here("figures_tables", "Table_S1.xlsx"), row.names = FALSE)

```

# Coverage Standardizing
## Figure S2

```{r iNEXT, fig.height=13, fig.width=12}

iNEXT_list <- as.list(NA)

for (i in 1:length(unique(Alpha_Diversity_df$SiteYear))) {
  xx <- Alpha_Diversity_df %>% filter(SiteYear == unique(Alpha_Diversity_df$SiteYear)[i]) %>% select(Quadrat, Acropora.spp, Astrea.spp, Astreopora.spp, Cladiella.spp, Dipsastraea.spp, Favites.spp, Fungiidae, Gardineroseris.planulata, Goniastrea.edwardsi, Goniastrea.stelligera, Hydnophora.exesa, Hydnophora.microconos, Leptastrea.spp, Leptoseris.myceteroides, Lobophyllia.spp, Lobophytum.spp, Montipora.spp, Pavona.duerdeni, Pavona.varians, Platygyra.spp, Pocillopora.spp, Porites.spp, Psammocora.profundacella, Sarcophyton.spp, Sinularia.spp, Turbinaria.spp)
  rownames(xx) <- xx$Quadrat
  xx$Quadrat<- NULL
  xx_t <- as.data.frame(t(xx))
  iNEXT_list[[i]] <- xx_t
  names(iNEXT_list)[i] <- unique(Alpha_Diversity_df$SiteYear)[i]
}

out.raw <- iNEXT(iNEXT_list, datatype="incidence_raw")
Figure_S2 <- ggiNEXT(out.raw, color.var ="Assemblage", se = FALSE) + 
  theme_DGM() + 
  theme(legend.position="bottom", legend.title=element_blank()) + 
  scale_color_manual(values = rainbow(34))
Figure_S2

# Run to save Figure S2
# jpeg(filename = here::here("figures_tables", "Figure_S2.jpeg"), width = 32, height = 40, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_S2
# dev.off()

```


## Extrapolation Trends
### Figure S3

```{r extrapolation plot, echo=FALSE, warning=FALSE, fig.height=7.5, fig.width=12}

extrapolation_df <- as.data.frame(matrix(data = NA, ncol = 2, nrow = length(50:99)))
colnames(extrapolation_df) <- c("Coverage", "Num_Extrapolated")
extrapolation_df$Coverage <- 50:99

for (i in 1:nrow(extrapolation_df)) {
  coverages <- 50:99
  j <- coverages[i]
  coverage_level <- as.numeric(paste("0", j, sep = "."))
  est_i <- estimateD(iNEXT_list, datatype="incidence_raw", base="coverage", level=coverage_level, conf=0.95)
  xx <- est_i %>% filter(Method == "Extrapolation")
  extrapolated_number <- length(unique(xx$Assemblage))
  extrapolation_df$Num_Extrapolated[i] <- extrapolated_number
}

extrapolation_df$Coverage <- as.numeric(extrapolation_df$Coverage)
extrapolation_df$Num_Extrapolated <- as.numeric(extrapolation_df$Num_Extrapolated)

Figure_S3 <- ggplot(extrapolation_df, aes(y=Num_Extrapolated, x=Coverage))  + labs(x="Percent coverage", y="Number of extrapolated sites") + theme_DGM() + geom_vline(xintercept = 90, color = "darkgreen", linetype='dashed', size=2) + geom_vline(xintercept = 85, color = "blue", linetype='dashed', size=2) + geom_vline(xintercept = 95, color = "blue", linetype='dashed', size=2) + ylim(0,30) + geom_point(size=4) + geom_line()
Figure_S3

#Run to save Figure S3
# jpeg(filename = here::here("figures_tables", "Figure_S3.jpeg"), width = 20, height = 15, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_S3
# dev.off()

```

# Hill Diversity 
## 85% Coverage
### Figure S4

```{r Coverage 85, fig.height=10, fig.width=16}

est.raw <- estimateD(iNEXT_list, datatype="incidence_raw", base="coverage", level=0.85, conf=0.95) 
estimates_85 <- est.raw %>% tidyr::separate(Assemblage, c("Site", "Year"), "_KI", remove = TRUE)

estimates_85$MHW <- NA
estimates_85$MHW[estimates_85$Year%in%before_years] <- "Before"
estimates_85$MHW[estimates_85$Year%in%after_years] <- "After"
estimates_85$MHW <- factor(estimates_85$MHW, levels = c("Before", "After"))

estimates_85$HD_Cont <- NA
estimates_85$NPP <- NA
for (i in 1:length(estimates_85$Site)) {
  xx <- Alpha_Diversity_df %>% filter(Site == estimates_85$Site[i])
  estimates_85$HD_Cont[i] <- xx$HD_Cont[1]
  estimates_85$NPP[i] <- xx$NPP[1]
}

Richness_85 <- estimates_85 %>% 
  filter(Order.q == 0) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() + labs(x="", y="Hill-Richness", title="") + 
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) + 
    theme(legend.position="none") + 
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Shannon_85 <- estimates_85 %>% 
  filter(Order.q == 1) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() +
    labs(x="", y="Hill-Shannon", title="") +
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    theme(legend.position="none") +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Simpson_85 <- estimates_85 %>% 
  filter(Order.q == 2) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() + 
    labs(x= "", y="Hill-Simpson", title="", shape = "MHW", color = "MHW") + 
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Diversity_85 <- plot_grid(Richness_85, Shannon_85, Simpson_85, labels = c("(a)", "(b)", "(c)"), nrow=1, rel_widths = c(1,1,1.3), label_size = 18)


Richness_diff_85 <- estimates_85 %>% 
  filter(Order.q == 0) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Shannon_diff_85 <- estimates_85 %>% 
  filter(Order.q == 1) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Simpson_diff_85 <- estimates_85 %>% 
  filter(Order.q == 2) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Richness_diff_Plot_85 <- Richness_diff_85 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="", y="Hill-Richness Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Shannon_diff_Plot_85 <- Shannon_diff_85 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="Local Anthropogenic Stress", y="Hill-Shannon Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Simpson_diff_Plot_85 <- Simpson_diff_85 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="", y="Hill-Simpson Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Difference_85 <- plot_grid(Richness_diff_Plot_85, Shannon_diff_Plot_85, Simpson_diff_Plot_85, NULL, labels = c("(d)", "(e)", "(f)", ""), nrow=1, rel_widths = c(1,1,1,0.3), label_size = 18)

Figure_S4 <- plot_grid(Diversity_85, Difference_85, ncol = 1)
Figure_S4

#Run to save Figure S4
# jpeg(filename = here::here("figures_tables", "Figure_S4.jpeg"), width = 40, height = 25, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_S4
# dev.off()

```


## 90% Coverage
### Figure 2

```{r Coverage 90, fig.height=5, fig.width=16}

est.raw <- estimateD(iNEXT_list, datatype="incidence_raw", base="coverage", level=0.90, conf=0.95) 
estimates_90 <- est.raw %>% tidyr::separate(Assemblage, c("Site", "Year"), "_KI", remove = TRUE)

estimates_90$MHW <- NA
estimates_90$MHW[estimates_90$Year%in%before_years] <- "Before"
estimates_90$MHW[estimates_90$Year%in%after_years] <- "After"
estimates_90$MHW <- factor(estimates_90$MHW, levels = c("Before", "After"))

# Very_High <- c("site27", "site30", "site32")
# High <- c("site26")
# Medium <- c("site1", "site34", "site35", "site6", "site8", "site14")
# Low <- c("site23", "site3", "site9")
# Very_Low <- c("site15", "site5", "site19", "site20")
# 
# estimates_90$HD_Cat <- NA
# estimates_90$HD_Cat[estimates_90$Site%in%Very_High] <- "Very High"
# estimates_90$HD_Cat[estimates_90$Site%in%High] <- "High"
# estimates_90$HD_Cat[estimates_90$Site%in%Medium] <- "Medium"
# estimates_90$HD_Cat[estimates_90$Site%in%Low] <- "Low"
# estimates_90$HD_Cat[estimates_90$Site%in%Very_Low] <- "Very Low"
# estimates_90$HD_Cat <- factor(estimates_90$HD_Cat, levels = c("Very Low", "Low","Medium", "High", "Very High"))


estimates_90$HD_Cont <- NA
estimates_90$NPP <- NA
estimates_90$HD_Cat <- NA
for (i in 1:length(estimates_90$Site)) {
  xx <- Alpha_Diversity_df %>% filter(Site == estimates_90$Site[i])
  estimates_90$HD_Cat[i] <- xx$HD_Cat
  estimates_90$HD_Cont[i] <- xx$HD_Cont[1]
  estimates_90$NPP[i] <- xx$NPP[1]
}

Richness_90 <- estimates_90 %>% 
  filter(Order.q == 0) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() + labs(x="", y="Hill-Richness", title="") + 
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) + 
    theme(legend.position="none") + 
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Shannon_90 <- estimates_90 %>% 
  filter(Order.q == 1) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() +
    labs(x="Local Anthropogenic Stress", y="Hill-Shannon", title="") +
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    theme(legend.position="none") +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Simpson_90 <- estimates_90 %>% 
  filter(Order.q == 2) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() + 
    labs(x= "", y="Hill-Simpson", title="", shape = "MHW", color = "MHW") + 
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Figure_2 <- plot_grid(Richness_90, Shannon_90, Simpson_90, labels = c("(a)", "(b)", "(c)"), nrow=1, rel_widths = c(1,1,1.3), label_size = 18)
Figure_2

#Run to save Figure 2
# jpeg(filename = here::here("figures_tables", "Figure_2.jpeg"), width = 40, height = 18, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_2
# dev.off()

```

### Figure S5

```{r Coverage 90 Figure S5, fig.height=10, fig.width=16}

Shannon_90_supp <- estimates_90 %>% 
  filter(Order.q == 1) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() +
    labs(x="", y="Hill-Shannon", title="") +
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    theme(legend.position="none") +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Diversity_90 <- plot_grid(Richness_90, Shannon_90_supp, Simpson_90, labels = c("(a)", "(b)", "(c)"), nrow=1, rel_widths = c(1,1,1.3), label_size = 18)

Richness_diff_90 <- estimates_90 %>% 
  filter(Order.q == 0) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Shannon_diff_90 <- estimates_90 %>% 
  filter(Order.q == 1) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Simpson_diff_90 <- estimates_90 %>% 
  filter(Order.q == 2) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Richness_diff_Plot_90 <- Richness_diff_90 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="", y="Hill-Richness Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Shannon_diff_Plot_90 <- Shannon_diff_90 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="Local Anthropogenic Stress", y="Hill-Shannon Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Simpson_diff_Plot_90 <- Simpson_diff_90 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="", y="Hill-Simpson Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Difference_90 <- plot_grid(Richness_diff_Plot_90, Shannon_diff_Plot_90, Simpson_diff_Plot_90, NULL, labels = c("(d)", "(e)", "(f)", ""), nrow=1, rel_widths = c(1,1,1,0.3), label_size = 18)

Figure_S5 <- plot_grid(Diversity_90, Difference_90, ncol = 1)
Figure_S5

#Run to save Figure S5
# jpeg(filename = here::here("figures_tables", "Figure_S5.jpeg"), width = 40, height = 25, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_S5
# dev.off()

```


## 95% Coverage
### Figure S6

```{r Coverage 95, fig.height=10, fig.width=16}

est.raw <- estimateD(iNEXT_list, datatype="incidence_raw", base="coverage", level=0.95, conf=0.95) 
estimates_95 <- est.raw %>% tidyr::separate(Assemblage, c("Site", "Year"), "_KI", remove = TRUE)

estimates_95$MHW <- NA
estimates_95$MHW[estimates_95$Year%in%before_years] <- "Before"
estimates_95$MHW[estimates_95$Year%in%after_years] <- "After"
estimates_95$MHW <- factor(estimates_95$MHW, levels = c("Before", "After"))

estimates_95$HD_Cont <- NA
estimates_95$NPP <- NA
for (i in 1:length(estimates_95$Site)) {
  xx <- Alpha_Diversity_df %>% filter(Site == estimates_95$Site[i])
  estimates_95$HD_Cont[i] <- xx$HD_Cont[1]
  estimates_95$NPP[i] <- xx$NPP[1]
}

Richness_95 <- estimates_95 %>% 
  filter(Order.q == 0) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() + labs(x="", y="Hill-Richness", title="") + 
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) + 
    theme(legend.position="none") + 
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Shannon_95 <- estimates_95 %>% 
  filter(Order.q == 1) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() +
    labs(x="", y="Hill-Shannon", title="") +
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    theme(legend.position="none") +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Simpson_95 <- estimates_95 %>% 
  filter(Order.q == 2) %>% 
  ggplot( aes(y=qD, x=HD_Cont, shape = MHW)) + 
    geom_point(aes(color = MHW), position = position_dodge(0.5), size = 5) + 
    theme_DGM() + 
    labs(x= "", y="Hill-Simpson", title="", shape = "MHW", color = "MHW") + 
    geom_errorbar(aes(ymax= qD.UCL, ymin= qD.LCL), position = position_dodge(0.5), width = 0.1) +
    ylim(-3,19) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), aes(color=MHW)) + 
    xlim(-1,86) + 
    scale_color_manual(values = c("#CC8B86", "#372549")) + 
    scale_shape_manual(values = c(17, 19)) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Diversity_95 <- plot_grid(Richness_95, Shannon_95, Simpson_95, labels = c("(a)", "(b)", "(c)"), nrow=1, rel_widths = c(1,1,1.3), label_size = 18)


Richness_diff_95 <- estimates_95 %>% 
  filter(Order.q == 0) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Shannon_diff_95 <- estimates_95 %>% 
  filter(Order.q == 1) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Simpson_diff_95 <- estimates_95 %>% 
  filter(Order.q == 2) %>% 
  select(Site, qD, MHW, HD_Cont) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Difference = Before - After)

Richness_diff_Plot_95 <- Richness_diff_95 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="", y="Hill-Richness Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Shannon_diff_Plot_95 <- Shannon_diff_95 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="Local Anthropogenic Stress", y="Hill-Shannon Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Simpson_diff_Plot_95 <- Simpson_diff_95 %>% 
  ggplot( aes(y=Difference, x=HD_Cont)) + 
    geom_point(size = 5, shape = 18) + 
    theme_DGM() + 
    labs(x="", y="Hill-Simpson Difference", title="") + 
    theme(legend.position="none") + 
    ylim(-1, 10) + 
    geom_smooth(method = 'lm', formula = y ~ poly(x,2), color="black") + 
    xlim(-1,86) + 
    theme(axis.title=element_text(size=20, face="bold"), axis.text = element_text(size=16, face="plain"))

Difference_95 <- plot_grid(Richness_diff_Plot_95, Shannon_diff_Plot_95, Simpson_diff_Plot_95, NULL, labels = c("(d)", "(e)", "(f)", ""), nrow=1, rel_widths = c(1,1,1,0.3), label_size = 18)

Figure_S6 <- plot_grid(Diversity_95, Difference_95, ncol = 1)
Figure_S6

#Run to save Figure S6
# jpeg(filename = here::here("figures_tables", "Figure_S6.jpeg"), width = 40, height = 25, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_S6
# dev.off()

```


# Modelling

## Table 1 and S3
- The following models were used to create Table 1 and S3

### Hill-Richness - 85% Coverage

```{r models 85 richness}

Richness_Model_85 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_85 %>% 
                               filter(Order.q == 0))
summary(Richness_Model_85)

```


### Hill-Shannon - 85% Coverage

```{r models 85 shannon}

Shannon_Model_85 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_85 %>% 
                              filter(Order.q == 1))
summary(Shannon_Model_85)

```


### Hill-Simpson - 85% Coverage

```{r models 85 simpson}

Simpson_Model_85 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_85 %>% 
                              filter(Order.q == 2))
summary(Simpson_Model_85)

```

### Hill-Richness - 90% Coverage

```{r models 90 richness}

Richness_Model_90 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_90 %>% 
                               filter(Order.q == 0))
summary(Richness_Model_90)

```

### Hill-Shannon - 90% Coverage

```{r models 90 shannon}

Shannon_Model_90 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_90 %>% 
                              filter(Order.q == 1))
summary(Shannon_Model_90)

```

### Hill-Simpson - 90% Coverage

```{r models 90 simpson}

Simpson_Model_90 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_90 %>% 
                              filter(Order.q == 2))
summary(Simpson_Model_90)

```

### Hill-Richness - 95% Coverage

```{r models 95 richness}

Richness_Model_95 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_95 %>% 
                               filter(Order.q == 0))
summary(Richness_Model_95)

```

### Hill-Shannon - 95% Coverage

```{r models 95 shannon}

Shannon_Model_95 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_95 %>% 
                              filter(Order.q == 1))
summary(Shannon_Model_95)

```

### Hill-Simpson - 95% Coverage

```{r models 95 simpson}

Simpson_Model_95 <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + NPP + (1|Site), data = estimates_95 %>% 
                              filter(Order.q == 2))
summary(Simpson_Model_95)

```

## NPP Sensitivity for 90% Coverage Models

### Hill-Richness - 90% Coverage

```{r models 90 richness no NPP}

Richness_Model_90_noNPP <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + (1|Site), data = estimates_90 %>% 
                               filter(Order.q == 0))
summary(Richness_Model_90_noNPP)

```

### Hill-Shannon - 90% Coverage

```{r models 90 shannon no NPP}

Shannon_Model_90_noNPP <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + (1|Site), data = estimates_90 %>% 
                              filter(Order.q == 1))
summary(Shannon_Model_90_noNPP)

```

### Hill-Simpson - 90% Coverage

```{r models 90 simpson no NPP}

Simpson_Model_90_noNPP <- glmmTMB(qD ~ poly(HD_Cont,2) * MHW + (1|Site), data = estimates_90 %>% 
                              filter(Order.q == 2))
summary(Simpson_Model_90_noNPP)

```

# Average Losses

## Table S4

```{r Average losses total}

#Richness
estimates_90 %>% 
  filter(Order.q == 0) %>% 
  select(Site, qD, MHW, HD_Cont, HD_Cat) %>% 
  pivot_wider(names_from = MHW, values_from = qD)%>% 
  mutate(Difference = Before - After) %>% 
  summarise(HillRichness = mean(Difference), SEM_HillRichness = (sd(Difference)/sqrt(length(Difference))))

#Shannon
estimates_90 %>% 
  filter(Order.q == 1) %>% 
  select(Site, qD, MHW, HD_Cont, HD_Cat) %>% 
  pivot_wider(names_from = MHW, values_from = qD)%>% 
  mutate(Difference = Before - After) %>% 
  summarise(HillShannon = mean(Difference), SEM_HillShannon = (sd(Difference)/sqrt(length(Difference))))

#Simpson
estimates_90 %>% 
  filter(Order.q == 2) %>% 
  select(Site, qD, MHW, HD_Cont, HD_Cat) %>% 
  pivot_wider(names_from = MHW, values_from = qD)%>% 
  mutate(Difference = Before - After) %>% 
  summarise(HillSimpson = mean(Difference), SEM_HillSimpson = (sd(Difference)/sqrt(length(Difference))))

```

```{r Average losses HD cat}

#Richness
Richness_Losses_90 <- estimates_90 %>% 
  filter(Order.q == 0) %>% 
  select(Site, qD, MHW, HD_Cont, HD_Cat) %>% 
  pivot_wider(names_from = MHW, values_from = qD) 

for (i in 1:length(Richness_Losses_90$Site)) {
  if(Richness_Losses_90$HD_Cat[i] == "High"){
    Richness_Losses_90$HD_Cat[i] <- "Very High"
  }
}

Table_S4 <- Richness_Losses_90 %>% 
  mutate(Difference = Before - After) %>% 
  group_by(HD_Cat) %>% 
  summarise(HillRichness = mean(Difference), SEM_HillRichness = (sd(Difference)/sqrt(length(Difference))))

#Shannon
Shannon_Losses_90 <- estimates_90 %>% 
  filter(Order.q == 1) %>% 
  select(Site, qD, MHW, HD_Cont, HD_Cat) %>% 
  pivot_wider(names_from = MHW, values_from = qD) 

for (i in 1:length(Shannon_Losses_90$Site)) {
  if(Shannon_Losses_90$HD_Cat[i] == "High"){
    Shannon_Losses_90$HD_Cat[i] <- "Very High"
  }
}

Shannon_avgLosses_90 <- Shannon_Losses_90 %>% 
  mutate(Difference = Before - After) %>% 
  group_by(HD_Cat) %>% 
  summarise(HillShannon = mean(Difference), SEM_HillShannon = (sd(Difference)/sqrt(length(Difference))))

Table_S4$HillShannon <- Shannon_avgLosses_90$HillShannon
Table_S4$SEM_HillShannon <- Shannon_avgLosses_90$SEM_HillShannon

#Simpson
Simpson_Losses_90 <- estimates_90 %>% 
  filter(Order.q == 2) %>% 
  select(Site, qD, MHW, HD_Cont, HD_Cat) %>% 
  pivot_wider(names_from = MHW, values_from = qD) 

for (i in 1:length(Simpson_Losses_90$Site)) {
  if(Simpson_Losses_90$HD_Cat[i] == "High"){
    Simpson_Losses_90$HD_Cat[i] <- "Very High"
  }
}

Simpson_avgLosses_90 <- Simpson_Losses_90 %>% 
  mutate(Difference = Before - After) %>% 
  group_by(HD_Cat) %>% 
  summarise(HillSimpson = mean(Difference), SEM_HillSimpson = (sd(Difference)/sqrt(length(Difference))))

Table_S4$HillSimpson <- Simpson_avgLosses_90$HillSimpson
Table_S4$SEM_HillSimpson <- Simpson_avgLosses_90$SEM_HillSimpson

Table_S4 %>%
  kbl() %>%
  kable_styling()

#Run to save Table S4 as an excel sheet
# write.xlsx(as.data.frame(Table_S4), here::here("figures_tables", "Table_S4.xlsx"), row.names = FALSE)

```

# Stressor Responses
Note: Notation in code is the same as the notation used in the manuscript equations.
## Figure 4 (a-c)
### (a) Richness

```{r Effect Size Richness, fig.height=6, fig.width=4}

Xdi_raw_Richness <- estimates_90 %>% 
  filter(Order.q == 0 & HD_Cat == "Very Low") %>% 
  group_by(Site) %>% 
  dplyr::select(Site, MHW, qD) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Xd_numerator = (Before - After)/Before)

Xd_Richness <- mean(Xdi_raw_Richness$Xd_numerator)

site_order_L2H <- c("VL2", "VL1", "VL5", "VL3", "L5", "L4", "L1", "M4", "M3", "M2", "M1", "M6", "M10", "H2", "VH2", "VH3", "VH1")

AR_Richness <- as.data.frame(matrix(data = NA, nrow = length(site_order_L2H), ncol = 7))
colnames(AR_Richness) <- c("Site", "HD_Cont", "Xci", "Xd", "Xai", "Xmi", "ARi")
AR_Richness$Xd <- Xd_Richness
AR_Richness$Site <- site_order_L2H

for (i in 1:nrow(AR_Richness)) {

  sub_df <- Alpha_Diversity_df %>% filter(Site == AR_Richness$Site[i])
  AR_Richness$HD_Cont[i] <- sub_df$HD_Cont[1]
  
  Yci <- estimates_90 %>% filter(Order.q == 0 & Site == AR_Richness$Site[i] & MHW == "Before") 
  Ymi <- estimates_90 %>% filter(Order.q == 0 & Site == AR_Richness$Site[i] & MHW == "After") 
  raw_calculations <- Xdi_raw_Richness %>% 
    mutate(Xci_numerator = (Before - Yci$qD[1])/Before, Xmi_numerator = (Before - Ymi$qD[1])/Before)
  
  AR_Richness$Xci[i] <- mean(raw_calculations$Xci_numerator)
  AR_Richness$Xmi[i] <- mean(raw_calculations$Xmi_numerator)
  
}


AR_Richness$Xai <- AR_Richness$Xci + AR_Richness$Xd
AR_Richness$ARi <- AR_Richness$Xmi - AR_Richness$Xai

fs.AR_Richness <- Fstats(ARi ~ HD_Cont, data = AR_Richness)
sctest(fs.AR_Richness)
breakpoints(fs.AR_Richness)

breakpoint_value <- AR_Richness$HD_Cont[9]

lm_Richness_lowHD <- lm(ARi ~ HD_Cont, data = subset(AR_Richness, HD_Cont <= 34.82568))
summary(lm_Richness_lowHD)
lm_Richness_preds_lowHD <- predict(lm_Richness_lowHD, interval = "confidence")

lm_Richness_highHD <- lm(ARi ~ HD_Cont, data = subset(AR_Richness, HD_Cont >= 34.82568))
summary(lm_Richness_highHD)
lm_Richness_preds_highHD <- predict(lm_Richness_highHD, interval = "confidence")

lm_Richness_preds_all <- rbind(lm_Richness_preds_lowHD, lm_Richness_preds_highHD)

AR_Richness <- cbind(AR_Richness, as.data.frame(lm_Richness_preds_all))

Figure_4a <- ggplot(AR_Richness, aes(x=HD_Cont, y=ARi)) + 
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=0, fill="#BE1E2D", alpha=0.4) + 
  annotate("rect", xmin=-Inf, xmax=Inf, ymax=Inf, ymin=0, fill="#F4D01E", alpha=0.4) + 
  labs(x= " ", y=" ", title="") + 
  theme_classic(base_size=14) + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title=element_text(size=16, face="bold"), axis.text = element_text(size=14, face="plain"), legend.text=element_text(size=14, face="plain"), legend.title = element_text(size=16, face="bold")) + 
  geom_ribbon( aes(ymin = lwr, ymax = upr), fill = "grey", alpha = 0.3, data=subset(AR_Richness, HD_Cont >= 34.82568)) + 
  geom_ribbon( aes(ymin = lwr, ymax = upr), fill = "grey", alpha = 0.3, data=subset(AR_Richness, HD_Cont <= 34.82568)) + 
  geom_line( aes(y = fit), size = 1, color = "black", linetype = "dashed", data=subset(AR_Richness, HD_Cont <= 34.82568)) + 
  geom_line( aes(y = fit), size = 1, color = "black", data=subset(AR_Richness, HD_Cont >= 34.82568)) + 
  geom_point(size=3, shape = 18) + 
  ylim(-1, 1)
Figure_4a

#Run to save Figure 4a
# jpeg(filename = here::here("figures_tables", "Figure_4a.jpeg"), width = 11.5, height = 16, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_4a
# dev.off()

```

### (b) Shannon
```{r Effect Size Shannon, fig.height=6, fig.width=4}

Xdi_raw_Shannon <- estimates_90 %>% 
  filter(Order.q == 1 & HD_Cat == "Very Low") %>% 
  group_by(Site) %>% 
  dplyr::select(Site, MHW, qD) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Xd_numerator = (Before - After)/Before)

Xd_Shannon <- mean(Xdi_raw_Shannon$Xd_numerator)

site_order_L2H <- c("VL2", "VL1", "VL5", "VL3", "L5", "L4", "L1", "M4", "M3", "M2", "M1", "M6", "M10", "H2", "VH2", "VH3", "VH1")

AR_Shannon <- as.data.frame(matrix(data = NA, nrow = length(site_order_L2H), ncol = 7))
colnames(AR_Shannon) <- c("Site", "HD_Cont", "Xci", "Xd", "Xai", "Xmi", "ARi")
AR_Shannon$Xd <- Xd_Shannon
AR_Shannon$Site <- site_order_L2H

for (i in 1:nrow(AR_Shannon)) {

  sub_df <- Alpha_Diversity_df %>% filter(Site == AR_Shannon$Site[i])
  AR_Shannon$HD_Cont[i] <- sub_df$HD_Cont[1]
  
  Yci <- estimates_90 %>% filter(Order.q == 1 & Site == AR_Shannon$Site[i] & MHW == "Before") 
  Ymi <- estimates_90 %>% filter(Order.q == 1 & Site == AR_Shannon$Site[i] & MHW == "After") 
  raw_calculations <- Xdi_raw_Shannon %>% 
    mutate(Xci_numerator = (Before - Yci$qD[1])/Before, Xmi_numerator = (Before - Ymi$qD[1])/Before)
  
  AR_Shannon$Xci[i] <- mean(raw_calculations$Xci_numerator)
  AR_Shannon$Xmi[i] <- mean(raw_calculations$Xmi_numerator)
  
}


AR_Shannon$Xai <- AR_Shannon$Xci + AR_Shannon$Xd
AR_Shannon$ARi <- AR_Shannon$Xmi - AR_Shannon$Xai

fs.AR_Shannon <- Fstats(ARi ~ HD_Cont, data = AR_Shannon)
sctest(fs.AR_Shannon)
breakpoints(fs.AR_Shannon)

lm_Shannon <- lm(ARi ~ HD_Cont, data = AR_Shannon)
summary(lm_Shannon)
lm_Shannon_preds <- predict(lm_Shannon, interval = "confidence")
AR_Shannon <- cbind(AR_Shannon, lm_Shannon_preds)

Figure_4b <- ggplot(AR_Shannon, aes(x=HD_Cont, y=ARi)) + 
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=0, fill="#BE1E2D", alpha=0.4) + 
  annotate("rect", xmin=-Inf, xmax=Inf, ymax=Inf, ymin=0, fill="#F4D01E", alpha=0.4) + 
  labs(x= " ", y=" ", title="") + 
  theme_classic(base_size=14) + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title=element_text(size=16, face="bold"), axis.text = element_text(size=14, face="plain"), legend.text=element_text(size=14, face="plain"), legend.title = element_text(size=16, face="bold")) + 
  geom_ribbon( aes(ymin = lwr, ymax = upr), fill = "grey", alpha = 0.3) + 
  geom_line( aes(y = fit), size = 1, color = "black", linetype = "dashed") + 
  geom_point(size=3, shape = 18) + 
  ylim(-1, 1)
Figure_4b

#Run to save Figure 4b
# jpeg(filename = here::here("figures_tables", "Figure_4b.jpeg"), width = 11.5, height = 16, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_4b
# dev.off()

```


### (c) Simpson
```{r Effect Size 2 Simpson, fig.height=6, fig.width=4}

Xdi_raw_Simpson <- estimates_90 %>% 
  filter(Order.q == 2 & HD_Cat == "Very Low") %>% 
  group_by(Site) %>% 
  dplyr::select(Site, MHW, qD) %>% 
  pivot_wider(names_from = MHW, values_from = qD) %>% 
  mutate(Xd_numerator = (Before - After)/Before)

Xd_Simpson <- mean(Xdi_raw_Simpson$Xd_numerator)

site_order_L2H <- c("VL2", "VL1", "VL5", "VL3", "L5", "L4", "L1", "M4", "M3", "M2", "M1", "M6", "M10", "H2", "VH2", "VH3", "VH1")

AR_Simpson <- as.data.frame(matrix(data = NA, nrow = length(site_order_L2H), ncol = 7))
colnames(AR_Simpson) <- c("Site", "HD_Cont", "Xci", "Xd", "Xai", "Xmi", "ARi")
AR_Simpson$Xd <- Xd_Simpson
AR_Simpson$Site <- site_order_L2H

for (i in 1:nrow(AR_Simpson)) {

  sub_df <- Alpha_Diversity_df %>% filter(Site == AR_Simpson$Site[i])
  AR_Simpson$HD_Cont[i] <- sub_df$HD_Cont[1]
  
  Yci <- estimates_90 %>% filter(Order.q == 2 & Site == AR_Simpson$Site[i] & MHW == "Before") 
  Ymi <- estimates_90 %>% filter(Order.q == 2 & Site == AR_Simpson$Site[i] & MHW == "After") 
  raw_calculations <- Xdi_raw_Simpson %>% 
    mutate(Xci_numerator = (Before - Yci$qD[1])/Before, Xmi_numerator = (Before - Ymi$qD[1])/Before)
  
  AR_Simpson$Xci[i] <- mean(raw_calculations$Xci_numerator)
  AR_Simpson$Xmi[i] <- mean(raw_calculations$Xmi_numerator)
  
}


AR_Simpson$Xai <- AR_Simpson$Xci + AR_Simpson$Xd
AR_Simpson$ARi <- AR_Simpson$Xmi - AR_Simpson$Xai

fs.AR_Simpson <- Fstats(ARi ~ HD_Cont, data = AR_Simpson)
sctest(fs.AR_Simpson)
breakpoints(fs.AR_Simpson)

lm_Simpson <- lm(ARi ~ HD_Cont, data = AR_Simpson)
summary(lm_Simpson)
lm_Simpson_preds <- predict(lm_Simpson, interval = "confidence")
AR_Simpson <- cbind(AR_Simpson, lm_Simpson_preds)

Figure_4c <- ggplot(AR_Simpson, aes(x=HD_Cont, y=ARi)) + 
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=0, fill="#BE1E2D", alpha=0.4) + 
  annotate("rect", xmin=-Inf, xmax=Inf, ymax=Inf, ymin=0, fill="#F4D01E", alpha=0.4) + 
  labs(x= " ", y=" ", title="") + 
  theme_classic(base_size=14) + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title=element_text(size=16, face="bold"), axis.text = element_text(size=14, face="plain"), legend.text=element_text(size=14, face="plain"), legend.title = element_text(size=16, face="bold")) + 
  geom_ribbon( aes(ymin = lwr, ymax = upr), fill = "grey", alpha = 0.3) + 
  geom_line( aes(y = fit), size = 1, color = "black", linetype = "dashed") + 
  geom_point(size=3, shape = 18) + 
  ylim(-1, 1)
Figure_4c

#Run to save Figure 4c
# jpeg(filename = here::here("figures_tables", "Figure_4c.jpeg"), width = 11.5, height = 16, units = "cm", pointsize = 15, quality = 600, res = 600)
# Figure_4c
# dev.off()

```





